---
title: "Report for column `r params$var` of dataset `r params$dataset`"
output: html_document
date: "2023-01-27"
params:
  dataset: mtcars
  var: "am"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Frequency table for `r params$var`

```{r, echo = F}
create_table <- function(dataset, var){

  dataset <- get(dataset)

  table(dataset[var]) |>
    knitr::kable()
}
```


The table below is for variable `r params$var` of 
dataset `r params$dataset`.

```{r}
create_table(params$dataset, params$var)
```

```{r, eval = FALSE, echo = FALSE}
# Run these lines to compile the document
# Set eval and echo to FALSE, so that this does not appear
# in the output, and does not get evaluated when knitting
rmarkdown::render(
             input = "tempelating parameterized reports.Rmd",
             params = list(
               dataset = "mtcars",
               var = "cyl"
             )
           )

```

I use lapply() to loop over a list of column names (that I get using colnames()). Because I don’t want to overwrite the report I need to change the name of the output file. I do so by using paste0() which creates a new string that contains the variable name, so each report gets its own name. x inside the paste0() function is each element, one after the other, of the columns variable I defined first.

```{r, eval = F, echo = F}
columns <- colnames(mtcars)

lapply(columns,
  (\(x)rmarkdown::render(
                    input = "param_report_example.Rmd",
                    output_file = paste0(
                      "param_report_example_", x, ".html"
                    ),
                    params = list(
                      dataset = "mtcars",
                      var = x
                    )
                  )
  )
)
```

